### 2023-01-17 README.Rmd

`clarify` implements simulation-based inference as an alternative to the delta method for computing functions of model parameters, such as average marginal effects. See the `clarify` [website](https://ngreifer.github.io/clarify) for documentation and other examples.

@@

You can install the development version of `clarify` from [GitHub](https://github.com/ngreifer/clarify) with:

``` r
# install.packages("devtools")
devtools::install_github("ngreifer/clarify")
```
## Introduction

>>>>

`clarify` implements simulation-based inference as an alternative to the delta method for computing functions of model parameters, such as average marginal effects. See the `clarify` [website](https://iqss.github.io/clarify) for documentation and other examples.

@@

You can install the development version of `clarify` from [GitHub](https://github.com/iqss/clarify) with:

``` r
# install.packages("devtools")
devtools::install_github("iqss/clarify")
```
## Introduction
